Power simulation section

### 2023-08-22 docs/manuscript.Rmd
Update manuscript.Rmd

affiliation:
  - id            : "1"
    institution   : "LMU Munich, Center for Leadership and People Management"
  - id            : "2"
    institution   : "LMU Munich, Department of Psychology"
  - id            : "3"
    institution   : "University of St. Gallen, Institute of Behavioral Science & Technology"
  - id            : "4"
    institution   : "University College London"

@@

abstract: |
  Understanding how humans interact with articifical intelligence (AI) through experiments becomes increasingly relevant. However, human-AI interaction researchers lack the appropriate tools to conduct power and data analyses for the required complex study designs. In this work, we provide a tutorial on how to run customized power analyses using data simulation based on Generalized Linear Mixed Models (GLMMs). By providing code in a specific case study, we equip human-AI interaction researchers with the tools to simulate their own data and run analyses based on GLMMs. We discuss implications for human-AI interaction research and provide an outlook on the relevance of power simulations in the field.

@@

<!-- General intro, relevance of Human AI Interaction experiments, need for well-powered and analyzed experimental research in this field -->
As the integration of artificial intelligence (AI) into our daily lives continues to grow, it has become increasingly important to study how humans interact with these intelligent systems. 
This is particularly important as AI becomes more sophisticated and is used in decision-making processes, for instance in medicine, that have significant impacts on individuals and society as a whole. 
Therefore, thorough experiments are needed to study human-AI interaction to understand how people perceive and respond to these novel technologies. 
When conducting experimental research in this emerging field, it is essential to determine an appropriate sample size [@lakensSampleSizeJustification2022] to ensure that the results obtained are both robust and informative, and use appropriate statistical models to analyze the data.

>>>>

affiliation:
  - id            : "1"
    institution   : "LMU Munich, Center for Leadership and People Management"
  - id            : "2"
    institution   : "LMU Munich, Department of Psychology"
  - id            : "3"
    institution   : "University of St. Gallen, Institute of Behavioral Science & Technology"
  - id            : "4"
    institution   : "University College London, Global Business School for Health"

@@

abstract: |
  Understanding how humans interact with artificial intelligence (AI) through experiments becomes increasingly relevant. However, human-AI interaction researchers often lack the appropriate tools to conduct power and data analyses for the complex study designs required. In this work, we provide a comprehensive guide to performing customized power analyses using data simulation based on Generalized Linear Mixed Models (GLMMs). By providing code in a specific case study, we equip human-AI interaction researchers with the tools to simulate their own data and run analyses based on GLMMs. We discuss implications for human-AI interaction research and provide an outlook on the relevance of power simulations in the field.

@@

<!-- General intro, relevance of Human AI Interaction experiments, need for well-powered and analyzed experimental research in this field -->
With the growing integration of artificial intelligence (AI) into our daily lives and routines, it has become increasingly important to study and understand how humans interact with these intelligent systems. 
This is particularly relevant as AI becomes more sophisticated and is deployed to support decision-making processes in fields such as law and medicine that have a significant impact on individuals and society at large. 
Therefore, thorough experimental research is needed to study human-AI interaction to understand how people perceive and respond to these novel technologies. 
When conducting experimental research in this emerging field, it is essential to determine an appropriate sample size [@lakensSampleSizeJustification2022] to ensure that the results obtained are both robust and informative, and use appropriate statistical models to analyze the data.
